Computer Science House Constitution

### 2022-02-17 constitution.tex
Reword candidate speeches
Co-authored-by: Max Meinhold <mxmeinhold@gmail.com>
remove opcomm

% ARTICLE V - EXECUTIVE BOARD
\article{Executive Board}
The Executive Board is the main governing body of the House.
Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
It is composed of the seven permanent directors and the Chairperson.
\\*\\*
There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an Executive Board member.
Ad Hoc directorships are created on an as-needed basis.
They are generally very task oriented and are chaired by a House member.
A directorship has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest.
Any large expenditures or large effect decisions must be brought before the entire House
\asection{Members of the Executive Board}
\asubsection{Voting Members}
\begin{itemize}
	\item Evaluations Director
	\item Social Director(s)
	\item Financial Director
	\item Research and Development Director(s)
	\item House Improvements Director
	\item Operational Communications Director
	\item House History Director
\end{itemize}
\asubsection{Non-Voting Members}
\begin{itemize}
	\item Chairperson
	\item House Secretary
	\item Ad Hoc Director(s)
\end{itemize}
\asection{Closed Executive Board}
Closed Executive Board Meetings are open only to the Chairperson, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
A closed Executive Board meeting may be called at any time by any member of the Executive Board.
However, the Chairperson and at least two-thirds of the Voting Members must be present for the meeting to be called.

@@

\asubsection{Responsibilities of the Research and Development Director}
\begin{enumerate}
	\item To preside over Research and Development Meetings in which House members are encouraged to bring ideas for projects
	\item To exercise general supervision over Research and Development operations
	\item To oversee the planning, organization and construction of technical projects for the House's benefit
	\item To collaborate with the Operational Communications Director in an attempt to fulfill the House's need for technical equipment
	\item To provide seminars and tutorials to educate House members in technical areas
\end{enumerate}

@@

\asubsection{Responsibilities of the Operational Communications Director}
\begin{enumerate}
	\item To represent the Root Type Persons at Executive Board Meetings and at House Meetings
	\item To report the status of the House computer systems and network to the Executive Board and House members
\end{enumerate}

@@

\asection{Operations}
\asubsection{Operations of the Financial Directorship}
\asubsubsection{Amount of House Dues}
The amount of dues for Active Members will be eighty dollars (\$80.00) per Academic Semester.
\asubsubsection{Collection of House Dues}
The collection period of house dues will be decided in conjunction with The Center for Residence Life and Housing Operations.
During the dues collection period, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
Dues for off-floor members are to be collected during this period as well by the Financial Director.
For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
Dues for any alumnus/alumnae in good standing are to be collected when intention to pay is expressed to the Financial Director.
\asubsubsubsection{Rules for Giving Exceptions and Exemptions for House Dues}
If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
If the Financial Director deems their situation appropriate, they may grant specific extensions or reductions of the member's payment as they see fit.
If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
If the Executive Board disagrees with the Financial Director, the Executive Board may reduce the required payment or extend the payment deadline.
If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
In the case the Financial Director or Executive Board decides the situation is appropriate, the member's dues may be partially or fully excused, or the member may be given additional time to pay their dues. 
Additional time and reduction of dues may both be given to a member in an appropriate situation.
All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}).
After this date, dues collection is suspended until the start of the next academic year.
\asubsubsection{Breakdown of Dues for Directorship Budgets}
\begin{center}
\begin{tabular}[c]{|l c|}
\hline
Directorship Name & Percentage of Dues \\
\hline
\hline
Operational Communications & 20\% \\
\hline
Evaluations \& Selections & 5\% \\
\hline
House History & 10\% \\
\hline
House Improvements & 15\% \\
\hline
Research and Development & 20\% \\
\hline
Social & 20\% \\
\hline
Accumulated & 10\% \\
\hline
\end{tabular}
\end{center}

@@

\asubsection{Operations of the Operational Communications Directorship}
The Operational Communications Directorship is responsible for overseeing the implementation of maintenance and upgrades to the House Computer Systems Network.
It is a self-governing committee making decisions by a simply majority vote.
Membership is composed of all Root Type Persons.

\asubsubsection{Selection of a Root Type Person}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Nominations are taken from the Root Type Persons and Prior Root Type Persons meeting the selection criteria in \ref{Qualifications of a Root Type Person}.
	\item Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
	\item A list of all nominees who have accepted is presented to the Executive Board for approval.
		This Executive Board Meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
	\item If an Executive Board member is a candidate for the office in discussion, the member is absent and their vote is abstained.
		A simple majority Executive Board vote, as described in \ref{Simple Majority}, is taken to determine whether the nominations of the Root Type Persons are accepted.
\end{enumerate}

\asubsubsection{Qualifications of a Root Type Person}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Candidates must have been an On-Floor Active Member in good standing within the last twelve months, or been an Off-Floor Active Member and have lived on the floor within the last twelve months.
	\item Candidates may be granted an exemption by current Root Type Persons.
		Such an exemption may be withdrawn at any time by the current Root Type Persons.
	\item Prior Root Type Persons are those members who are no longer current Active Members and have not been granted an extension by the current Root Type Persons.
		Prior Root Type Persons are not guaranteed access to the current root passwords and other authentication tokens.
	\item The current Root Type Persons may from time to time draft rules and regulations specifying the rights and privileges of Prior Root Type Persons.
\end{enumerate}

\asubsubsection{Creation of Accounts}
Root Type Persons have the authority to manage user accounts for House systems.
Before introductory, active, or alumni members may receive an account they must:
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
\end{enumerate}
Accounts for honorary and advisory members may be created at the discretion of the Root Type Persons.

\asubsubsection{Code of Conduct}
The Code of Conduct located at \url{https://github.com/ComputerScienceHouse/CodeOfConduct} is the canonical Code of Conduct for Computer Science House accounts.
\\* \\*
Members are bound to the Code of Conduct revision that they sign when initially creating their account.
Members may sign a more recent revision of the Code of Conduct to update their agreement.
\asubsubsubsection{Changes}
The following process is used for making changes to the Code of Conduct document.
\begin{enumerate}
	\item A Root Type Person drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
	\item The change is proposed at a House Meeting and is discussed at the same House Meeting.
	\item The final proposal is presented at the next House Meeting and ballots are distributed for a Balloted House vote as described in \ref{Balloted Vote}.
\end{enumerate}

\asection{Qualifications}
\asubsection{Qualifications to be the Chairperson, Evaluations Director}
\begin{enumerate}
	\item Candidates must be Active Members during the term of office
	\item Candidates must reside on floor during the term of office
	\item Candidates must have at least one full semester of House membership as an Active Member
	\item Elected or selected candidates may not hold a simultaneous voting Executive Board position, and must therefore resign their current position, or the position of Chairperson, should they be elected
\end{enumerate}
\asubsection{Qualifications to be the Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director}
\begin{enumerate}
	\item Candidates must be Active Members during the term of office
	\item Candidates must have at least one full semester of House membership as an Active Member
	\item Elected or selected candidates may not hold two simultaneous voting Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position
\end{enumerate}
\asubsection{Qualifications to be the Operational Communications Director}
\begin{enumerate}
	\item Candidates must be a current Root Type Person \ref{Operations of the Operational Communications Directorship}.
	\item Candidates must be a current Active Member.
	\item A Root Type Person cannot be the director if they currently hold any other voting Executive Board Position.
\end{enumerate}

@@

The following special cases cover the operation of a dual directorship:
\begin{itemize}
	\item If one of the members in a dual directorship resigns the directorship, or for any other reason ends the term of office, the other member in the dual directorship must also step down and the office becomes vacated.
		The vacated office is then handled like any other vacated office; see \ref{Executive Board Resignations}.
	\item During an official Executive Board Vote, each dual directorship member's vote counts for one-half vote in the tallying of votes.
		The members of the dual directorship need not vote the same way in a vote.
	\item A member of a dual directorship may not hold any other Executive Board position.
	\item When attendance requirements call for the dual directorship position to be present, both dual directorship members are to fulfill the requirements.
\end{itemize}
\asubsection{Selection of the Chairperson, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, House History Director, Research and Development Director(s)}
	\item The opening of the Executive Board position(s) is announced at a House meeting and nominations for the position are taken for a minimum of a seventy-two hour period.
		Any House member may nominate any member or pair of members where appropriate for a Directorship.
	\item The candidates will be notified of their nomination.
		Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
		A list of all nominees who have accepted their nominations will be posted shortly thereafter.
	\item Each candidate will be given an equal amount of time before the House to present their platform of candidacy.
	\item Ballots will then be distributed and voting will be open for a minimum of a forty-eight hour period.
		The Ballots will list, in random order, all of the candidates who are qualified for a given office with a means to indicate the selection of one of the candidates.
		In addition, an area will be provided to indicate a write-in selection of a candidate.
	\item At the end of the voting period, the Chairperson will terminate voting by collecting the ballot box and the votes shall be counted as stated in \ref{Alternative Vote}.
	\item The winners are determined via the process described in \ref{Alternative Vote}.
		A quorum of fifty-percent of the number of all members eligible to vote is required for the election to be official.
		All winners are notified of their election.
		If the position is currently vacant, the winner immediately assumes office.
		If not, the winner will assume office at the end of the current term (\ref{Term}).
		Any office whose winner declines the election, or whose winner does not fulfill the requirements of the elected office, shall have their votes redistributed in the same process as a loser in \ref{Alternative Vote}.
\asubsection{Selection of the Operational Communications Director}
	\item A candidate for the Operational Communications Directorship shall be chosen by the current Root Type Persons.
	\item The candidate is given a minimum of twenty-four hours to accept or decline the nomination.
	\item The candidate is presented to the Executive Board for approval.
		This Executive Board meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
	\item All current Executive Board Voting Members must be present during the discussion and voting period unless that member is a candidate for the position, in which case the member is absent and their vote is abstained.
		A simple majority Executive Board vote, as described in \ref{Simple Majority}, is taken to determine whether the candidate is selected for the position.
\asubsection{Selection of Ad Hoc Directors}
	\item When the Executive Board or a group of House members feels an Ad Hoc Directorship is necessary, they present their plans to the Executive Board and the Executive Board decides by simple majority vote whether directorship status is granted.
	\item When the Ad Hoc Directorship is granted status, a director is appointed, and duties, budgetary, and membership considerations are defined.
\asubsection{Selection of the House Secretary}
The Executive Board may choose to select a current voting Executive Board member, or to select any interested Active member, as House Secretary.
The selection process can be an informal appointment, or follow an election process similar to other voting Executive Board positions.

>>>>

% ARTICLE V - EXECUTIVE BOARD
\article{Executive Board}
The Executive Board is the main governing body of the House.
Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
It is composed of the seven permanent directors and the Chairperson.
\\*\\*
There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an Executive Board member.
Ad Hoc directorships are created on an as-needed basis.
They are generally very task oriented and are chaired by a House member.
A directorship has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest.
Any large expenditures or large effect decisions must be brought before the entire House
\asection{Members of the Executive Board}
\asubsection{Voting Members}
\begin{itemize}
	\item Evaluations Director
	\item Social Director(s)
	\item Financial Director
	\item Research and Development Director(s)
	\item House Improvements Director
	\item House History Director
\end{itemize}
\asubsection{Non-Voting Members}
\begin{itemize}
	\item Chairperson
	\item House Secretary
	\item Ad Hoc Director(s)
\end{itemize}
\asection{Closed Executive Board}
Closed Executive Board Meetings are open only to the Chairperson, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
A closed Executive Board meeting may be called at any time by any member of the Executive Board.
However, the Chairperson and at least two-thirds of the Voting Members must be present for the meeting to be called.

@@

\asubsection{Responsibilities of the Research and Development Director}
\begin{enumerate}
	\item To preside over Research and Development Meetings in which House members are encouraged to bring ideas for projects
	\item To exercise general supervision over Research and Development operations
	\item To oversee the planning, organization and construction of technical projects for the House's benefit
	\item To provide seminars and tutorials to educate House members in technical areas
\end{enumerate}

@@

@@

\asection{Operations}
\asubsection{Operations of the Financial Directorship}
\asubsubsection{Amount of House Dues}
The amount of dues for Active Members will be eighty dollars (\$80.00) per Academic Semester.
\asubsubsection{Collection of House Dues}
The collection period of house dues will be decided in conjunction with The Center for Residence Life and Housing Operations.
During the dues collection period, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
Dues for off-floor members are to be collected during this period as well by the Financial Director.
For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
Dues for any alumnus/alumnae in good standing are to be collected when intention to pay is expressed to the Financial Director.
\asubsubsubsection{Rules for Giving Exceptions and Exemptions for House Dues}
If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
If the Financial Director deems their situation appropriate, they may grant specific extensions or reductions of the member's payment as they see fit.
If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
If the Executive Board disagrees with the Financial Director, the Executive Board may reduce the required payment or extend the payment deadline.
If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
In the case the Financial Director or Executive Board decides the situation is appropriate, the member's dues may be partially or fully excused, or the member may be given additional time to pay their dues. 
Additional time and reduction of dues may both be given to a member in an appropriate situation.
All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}).
After this date, dues collection is suspended until the start of the next academic year.
\asubsubsection{Breakdown of Dues for Directorship Budgets}
\begin{center}
\begin{tabular}[c]{|l c|}
\hline
Directorship Name & Percentage of Dues \\
\hline
\hline
Evaluations \& Selections & 5\% \\
\hline
House History & 15\% \\
\hline
House Improvements & 20\% \\
\hline
Research and Development & 25\% \\
\hline
Social & 25\% \\
\hline
Accumulated & 10\% \\
\hline
\end{tabular}
\end{center}

@@

\asubsubsection{Creation of Accounts}
Executive Members have the authority to manage user accounts for House systems.
Before introductory, active, or alumni members may receive an account they must:
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
\end{enumerate}
Accounts for honorary and advisory members may be created at the discretion of Executive Board.

\asubsubsection{Code of Conduct}
The Code of Conduct located at \url{https://github.com/ComputerScienceHouse/CodeOfConduct} is the canonical Code of Conduct for Computer Science House accounts.
\\* \\*
Members are bound to the Code of Conduct revision that they sign when initially creating their account.
Members may sign a more recent revision of the Code of Conduct to update their agreement.
\asubsubsubsection{Changes}
The following process is used for making changes to the Code of Conduct document.
\begin{enumerate}
	\item A Active Member drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
	\item The change is proposed at a House Meeting and is discussed at the same House Meeting.
	\item The final proposal is presented at the next House Meeting and ballots are distributed for a Balloted House vote as described in \ref{Balloted Vote}.
\end{enumerate}

\asection{Qualifications}
\asubsection{Qualifications to be the Chairperson, Evaluations Director}
\begin{enumerate}
	\item Candidates must be Active Members during the term of office
	\item Candidates must reside on floor during the term of office
	\item Candidates must have at least one full semester of House membership as an Active Member
	\item Elected or selected candidates may not hold a simultaneous voting Executive Board position, and must therefore resign their current position, or the position of Chairperson, should they be elected
\end{enumerate}
\asubsection{Qualifications to be the Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director}
\begin{enumerate}
	\item Candidates must be Active Members during the term of office
	\item Candidates must have at least one full semester of House membership as an Active Member
	\item Elected or selected candidates may not hold two simultaneous voting Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position
\end{enumerate}

@@

The following special cases cover the operation of a dual directorship:
\begin{itemize}
	\item If one of the members in a dual directorship resigns the directorship, or for any other reason ends the term of office, the other member in the dual directorship must also step down and the office becomes vacated.
		The vacated office is then handled like any other vacated office; see \ref{Executive Board Resignations}.
	\item During an official Executive Board Vote, each dual directorship member's vote counts for one-half vote in the tallying of votes.
		The members of the dual directorship need not vote the same way in a vote.
	\item A member of a dual directorship may not hold any other Executive Board position.
	\item When attendance requirements call for the dual directorship position to be present, both dual directorship members are to fulfill the requirements.
\end{itemize}
\asubsection{Selection of the Chairperson, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, House History Director, Research and Development Director(s)}
\begin{enumerate}
	\item The opening of the Executive Board position(s) is announced at a House meeting and nominations for the position are taken for a minimum of a seventy-two hour period.
		Any House member may nominate any member or pair of members where appropriate for a Directorship.
	\item The candidates will be notified of their nomination.
		Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
		A list of all nominees who have accepted their nominations will be posted shortly thereafter.
	\item Each candidate will be given an equal amount of time before the House to present their platform of candidacy.
	\item Ballots will then be distributed and voting will be open for a minimum of a forty-eight hour period.
		The Ballots will list, in random order, all of the candidates who are qualified for a given office with a means to indicate the selection of one of the candidates.
		In addition, an area will be provided to indicate a write-in selection of a candidate.
	\item At the end of the voting period, the Chairperson will terminate voting by collecting the ballot box and the votes shall be counted as stated in \ref{Alternative Vote}.
	\item The winners are determined via the process described in \ref{Alternative Vote}.
		A quorum of fifty-percent of the number of all members eligible to vote is required for the election to be official.
		All winners are notified of their election.
		If the position is currently vacant, the winner immediately assumes office.
		If not, the winner will assume office at the end of the current term (\ref{Term}).
		Any office whose winner declines the election, or whose winner does not fulfill the requirements of the elected office, shall have their votes redistributed in the same process as a loser in \ref{Alternative Vote}.
\end{enumerate}

\asubsection{Selection of Ad Hoc Directors}
\begin{enumerate}
	\item When the Executive Board or a group of House members feels an Ad Hoc Directorship is necessary, they present their plans to the Executive Board and the Executive Board decides by simple majority vote whether directorship status is granted.
	\item When the Ad Hoc Directorship is granted status, a director is appointed, and duties, budgetary, and membership considerations are defined.
\end{enumerate}
\asubsection{Selection of the House Secretary}
The Executive Board may choose to select a current voting Executive Board member, or to select any interested Active member, as House Secretary.
The selection process can be an informal appointment, or follow an election process similar to other voting Executive Board positions.
